\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-04-04 flux.tex

%%% smith_comparison %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison}
	\caption{\textbf{Comparison of A/H3N3 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an equivalent BMDS model.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from an equivalent BMDS model.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a Uniform$(-100,100)$ prior on antigenic locations and serum effects fixed at maximum titer values. 
	} 
	\label{smith_comparison} 
\end{figure}

@@

%%% smith_comparison_rotation %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison_rotation}
	\caption{\textbf{Comparison of A/H3N3 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an equivalent BMDS model under an alternative solution.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from an equivalent BMDS model that has converged on the alternative solution.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a Uniform$(-100,100)$ prior on antigenic locations and serum effects fixed at maximum titer values. 	
	} 
	\label{smith_comparison_rotation} 
\end{figure}

@@

%%% smith_comparison_drift %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison_drift}
	\caption{\textbf{Comparison of A/H3N3 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an extended BMDS model that includes date-informed priors on antigenic locations.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from a BMDS model that includes date-informed priors on antigenic locations.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a date-informed prior on antigenic locations and serum effects fixed at maximum titer values. 	
	} 
	\label{smith_comparison_drift} 
\end{figure}

@@

%%% smith_comparison_effects %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison_effects}
	\caption{\textbf{Comparison of A/H3N3 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an extended BMDS model that estimates serum and virus effects.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from a BMDS model that estimates virus and serum effects.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a Uniform$(-100,100)$ prior on antigenic locations and virus and serum effects estimated in a hierarchical Bayesian fashion. 	
	} 
	\label{smith_comparison_effects} 
\end{figure}

>>>>

%%% smith_comparison %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison}
	\caption{\textbf{Comparison of A/H3N2 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an equivalent BMDS model.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from an equivalent BMDS model.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a Uniform$(-100,100)$ prior on antigenic locations and serum effects fixed at maximum titer values. 
	} 
	\label{smith_comparison} 
\end{figure}

@@

%%% smith_comparison_rotation %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison_rotation}
	\caption{\textbf{Comparison of A/H3N2 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an equivalent BMDS model under an alternative solution.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from an equivalent BMDS model that has converged on the alternative solution.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a Uniform$(-100,100)$ prior on antigenic locations and serum effects fixed at maximum titer values. 	
	} 
	\label{smith_comparison_rotation} 
\end{figure}

@@

%%% smith_comparison_drift %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison_drift}
	\caption{\textbf{Comparison of A/H3N2 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an extended BMDS model that includes date-informed priors on antigenic locations.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from a BMDS model that includes date-informed priors on antigenic locations.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a date-informed prior on antigenic locations and serum effects fixed at maximum titer values. 	
	} 
	\label{smith_comparison_drift} 
\end{figure}

@@

%%% smith_comparison_effects %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=1.0\textwidth]{figures/smith_comparison_effects}
	\caption{\textbf{Comparison of A/H3N2 antigenic locations estimated by Smith et al.\ \cite{Smith04} using MDS and an extended BMDS model that estimates serum and virus effects.} 
	(A) MDS antigenic locations, reorientated so that the primary dimension lies on the $x$-axis rather than on the $y$-axis as in Figure 1 of \cite{Smith04}.
	(B) A posterior sample of antigenic locations from a BMDS model that estimates virus and serum effects.
	In (A) and (B), viruses are shown as colored circles, with color denoting antigenic cluster inferred by \cite{Smith04}, and sera are shown as gray points.
	(C) Antigenic distances between A/Bilthoven/16190/1968 and all other viruses determined for both methods.
	(D) Antigenic distances between A/Fujian/411/2002 and all other viruses determined for both methods.
	(E) Antigenic distances between 750 random pairs of viruses determined for both methods.	
	In (C), (D) and (E) red points show distances for the MDS model and gray bars show the 95\% credible interval of distances for the BMDS model, while the red dashed line shows a LOESS regression to MDS distances, and the black dashed line shows a LOESS regression to the BMDS distances.
	The BMDS model has a Uniform$(-100,100)$ prior on antigenic locations and virus and serum effects estimated in a hierarchical Bayesian fashion. 	
	} 
	\label{smith_comparison_effects} 
\end{figure}
